\chapter{Introduction}

An internship is a professional learning experience that offers meaningful, practical work related to a student’s field of study or career interest.
An internship gives a student the opportunity for career exploration and development, and to learn new skills.
It offers the employer the opportunity to bring new ideas and energy into the workplace, develop talent and potentially build a pipeline for future full-time employees.
Internships are usually offered part-time if it is during a university semester, or full-time if it is during a vacation.
And in most of the cases, the internship is paid. \\

Institute of Information and Communication Technology, SUST always emphasizes industry knowledge on academic study. 
And to give students actual industry experience, IICT provides the opportunity to their students of Department of Software Engineering to work as an intern for six-months in a renowned software company as a part of their academic curriculum in the 7th semester.
This opportunity helps to add a great value to personal qualification and experiences of their students. \\

The company I was sent to for my internship is Kaz Software. It is one of the most experienced software company in Bangladesh. Kaz Software have been successfully operating for more than 18 years.

\section{Objective}

This report is prepared as a requirement of the course SWE 420 at Department of software Engineering, Institute of Information and Communication Technology, SUST. \\

This document is intended to contain achievement, learnings, professional growth, achievements, and overall industrial experience during my internship period. \\

And if it is allowed, this document will be open to other students who'll be working as interns in future.
So that they can decide if Kaz Software is a good choice for them.

\section{Scope}

The main scopes of this document are:

\begin{enumerate}
    \item Work environment and culture of Kaz Software
    \item Experiences I faced as an intern of Kaz Software
    \item Projects I have worked on during my internship
    \item The training and guidance I received
    \item My professional and technical growth
    \item Description of the technologies I used during my internship
    \item And my opinion on this internship
\end{enumerate}

Everything is discussed in this document without violating the confidentiality of the company.

\section{Sources of Information}

All of the information reported in this document is true and authentic.
The accuracy and confidentiality of the information related to the company is verified by executives of Kaz Software.\\

This document contains both technical and theoretical information.
As a result some information is taken from various websites, and the links to that websites are attached at the end of this report.
So that reader can manually verify any external information, if they have any doubt.

\section{Limitations}

There are some limitations in this report.
Not everything I did during my internship period can be shared with outside world.
This document is reviewed by an executive from my company several times before submitting.
And during those reviews, several information have been omitted, because they are confidential to Kaz Software.
As a result this document is not perfect.