\chapter{Conclusion}

I view this six-month internship as the most important part of my undergraduate education.
Thanks to the internship program, I learned a lot about the software industry, its culture, workplace, and everything related to software development.
My knowledge was expanded, connections between my academic and professional experiences were made, and my room for progress was identified.
I became familiar with the professional company culture and the technology they use through the internship program.
My internship taught me the importance of professionalism and patience.\\

It also taught me about the software life cycle that is employed in the software industry and motivated me to work hard, be accountable, and have confidence in myself.
My ability to work in a team and communicate effectively, as well as my respect for the opinions and suggestions of my teammates, have all improved as a result of the internship program.
I was able to identify and resolve a number of problems that would not have been possible without team discussions and brainstorming sessions.\\

Despite the fact that I did work as an intern at Kaz Software, most of the time I was treated more like a full-time employee.
I received all the benefits of a full-time employee.
Interns typically receive mock assignments and are prohibited from working on real life projects, at least for a time.
As opposed to myself, who began working on a real-world project on the first day of my internship.
And on occasion, I was required to research a new technology or problem.
These, in my opinion, helped me learn more and stoked my desire to study more.\\

From my perspective, I would suggest Kaz Software for both internships and full-time jobs if you want to learn and develop in a fun and happy way.
I would like to express my gratitude to the Institute of Information and Communication Technology for giving me this wonderful opportunity and to my teammates for making me feel at home even when I was at work.
Undoubtedly, it is a significant accomplishment that will aid in my progression toward a professional life.